Enhancement of SDR in Thessaloniki

### 2024-05-08 GHI_enh_CSid.tex
Commit 2024-05-08 22:14

\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}

@@

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-27}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\texttt{Low\_B.Low\_W.glo} has compensation for sun distance, TSI variation and Kurudz difference

@@

\NormalTok{DTdaily }\OtherTok{\textless{}{-}}\NormalTok{ DATA[,}
\NormalTok{                .(}
                  \AttributeTok{glo\_Sum   =} \FunctionTok{sum}\NormalTok{(Low\_B.Low\_W.glo),}
                  \AttributeTok{GLB\_Sum   =} \FunctionTok{sum}\NormalTok{(wattGLB),}
                  \AttributeTok{GLB\_N     =} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wattGLB)),}
                  \AttributeTok{DayLength =} \FunctionTok{max}\NormalTok{(DayLength),}
\NormalTok{                  .N}
\NormalTok{                ),}
\NormalTok{                by }\OtherTok{=}\NormalTok{ Day]}

\FunctionTok{hist}\NormalTok{(DTdaily}\SpecialCharTok{$}\NormalTok{GLB\_N)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{hist}\NormalTok{(DTdaily[, GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength])}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# plot(DTdaily[, GLB\_N/DayLength, Day])}
\FunctionTok{summary}\NormalTok{(DTdaily[, GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength])}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# remove days with few relative data}
\NormalTok{Daytime\_Ratio }\OtherTok{\textless{}{-}} \FloatTok{0.3}

\NormalTok{DTdaily }\OtherTok{\textless{}{-}}\NormalTok{ DATA[,}
\NormalTok{                .(}
                  \AttributeTok{glo\_Sum   =} \FunctionTok{sum}\NormalTok{(Low\_B.Low\_W.glo),}
                  \AttributeTok{GLB\_Sum   =} \FunctionTok{sum}\NormalTok{(wattGLB),}
                  \AttributeTok{GLB\_N     =} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wattGLB)),}
                  \AttributeTok{DayLength =} \FunctionTok{max}\NormalTok{(DayLength),}
\NormalTok{                  .N}
\NormalTok{                ),}
\NormalTok{                by }\OtherTok{=}\NormalTok{ Day]}

\NormalTok{DTyear }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}\AttributeTok{glo =} \FunctionTok{mean}\NormalTok{(Low\_B.Low\_W.glo),}
                   \AttributeTok{GLB =} \FunctionTok{mean}\NormalTok{(wattGLB),}
\NormalTok{                   .N),}
\NormalTok{               by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date))]}

\FunctionTok{plot}\NormalTok{(DTyear[, N, year], }\AttributeTok{col =} \StringTok{"blue"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot}\NormalTok{(DTyear[, GLB}\SpecialCharTok{/}\NormalTok{glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\StringTok{"Clear GLB / CS libratran by year"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{DTmonth }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}\AttributeTok{glo =} \FunctionTok{mean}\NormalTok{(Low\_B.Low\_W.glo),}
                    \AttributeTok{GLB =} \FunctionTok{mean}\NormalTok{(wattGLB),}
\NormalTok{                    .N),}
\NormalTok{                by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date), }\FunctionTok{month}\NormalTok{(Date))]}
\NormalTok{DTmonth[, tsy }\SpecialCharTok{:=}\NormalTok{ year }\SpecialCharTok{+}\NormalTok{ (month }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)}\SpecialCharTok{/}\DecValTok{12}\NormalTok{ ]}

\CommentTok{\# plot(  DTmonth[, .N, tsy], col = "blue")}
\FunctionTok{plot}\NormalTok{(  DTmonth[, GLB}\SpecialCharTok{/}\NormalTok{glo, tsy], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\StringTok{"Clear GLB / CS libratran by month"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{out.height =} \StringTok{"32\%"}\NormalTok{   )}

\ControlFlowTok{for}\NormalTok{ (ad }\ControlFlowTok{in} \FunctionTok{sort}\NormalTok{(days)) \{}
\NormalTok{  temp }\OtherTok{\textless{}{-}}\NormalTok{ DATA[Day }\SpecialCharTok{==}\NormalTok{ ad,]}

\NormalTok{  ylim }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(temp[, Low\_B.Low\_W.glo, wattGLB])}

  \FunctionTok{plot}\NormalTok{(  temp[, Low\_B.Low\_W.glo, Date],}
         \AttributeTok{col =} \StringTok{"blue"}\NormalTok{,}
         \AttributeTok{ylim =}\NormalTok{ ylim)}
  \FunctionTok{points}\NormalTok{(temp[, wattGLB, Date], }\AttributeTok{col =} \StringTok{"green"}\NormalTok{)}
  \FunctionTok{title}\NormalTok{(}\FunctionTok{as.Date}\NormalTok{(ad, }\AttributeTok{origin =} \StringTok{"1970{-}01{-}01"}\NormalTok{))}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

@@

@@

>>>>

\usepackage{bookmark}

@@

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-08}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\texttt{Low\_B.Low\_W.glo} has compensation for sun distance, TSI variation and Kurudz difference only

@@

\FunctionTok{source}\NormalTok{(}\StringTok{"./GHI\_enh\_Aeronet.R"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Cross over point: 2005 
\end{verbatim}

@@

@@

@@

@@

@@

@@

\begin{verbatim}
SZA min : 0.00137165912186399 
\end{verbatim}

@@

\begin{verbatim}
SZA mean : 0.0020024477410843 
\end{verbatim}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-47} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-48} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-49} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-50} \end{center}

\begin{verbatim}
SZA median : 0.00184853525463023

\newpage
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-51} \end{center}

\newpage
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-52} \end{center}

\newpage
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{DATA[, tsy }\SpecialCharTok{:=} \FunctionTok{year}\NormalTok{(Date) }\SpecialCharTok{+}\NormalTok{ (}\FunctionTok{month}\NormalTok{(Date) }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)}\SpecialCharTok{/}\DecValTok{12}\NormalTok{ ]}

\DocumentationTok{\#\# apply AOD trend}
\NormalTok{trendsf }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(trend\_median, trend\_mean, trend\_min)}

\NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_median}
\NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_mean}

\NormalTok{trend\_factor }\OtherTok{\textless{}{-}} \FloatTok{0.86}

\NormalTok{DATA[, Thresh\_test }\SpecialCharTok{:=}\NormalTok{ Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{*}\NormalTok{ trend\_factor)]}

\FunctionTok{rmserr}\NormalTok{(DATA}\SpecialCharTok{$}\NormalTok{Enhanc\_C\_4\_ref, DATA}\SpecialCharTok{$}\NormalTok{wattGLB)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
$mae
[1] 94.57364

$mse
[1] 10035.43

$rmse
[1] 100.177

$mape
[1] 0.1485271

$nmse
[1] 0.1642926

$rstd
[1] 0.1495398
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{f }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x) \{}

\NormalTok{  test }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}
    \FunctionTok{mean}\NormalTok{(Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{*}\NormalTok{ x)),}
    \FunctionTok{mean}\NormalTok{(wattGLB)),}
\NormalTok{       by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date), }\FunctionTok{month}\NormalTok{(Date))]}

  \CommentTok{\# DATA[, sum( abs((Enhanc\_C\_4\_ref * (1 + trend\_apply(tsy) * x)) {-} wattGLB)) ]}

  \CommentTok{\# DATA[, sum(1 {-} (Enhanc\_C\_4\_ref * (1 + trend\_apply(tsy) * x) / wattGLB)) ]}

  \FunctionTok{rmserr}\NormalTok{(test}\SpecialCharTok{$}\NormalTok{V1, test}\SpecialCharTok{$}\NormalTok{V2)}\SpecialCharTok{$}\NormalTok{mse}
  \CommentTok{\# test[, sum(V1 {-} V2)]}
\NormalTok{\}}

\FunctionTok{optimise}\NormalTok{(f, }\AttributeTok{interval =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.2}\NormalTok{, }\FloatTok{1.8}\NormalTok{), }\AttributeTok{maximum =}\NormalTok{ F, }\AttributeTok{tol =} \FloatTok{0.0001}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
$minimum
[1] 0.2000654

$objective
[1] 8644.06
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# optim(0.8, f, method = "Brent", lower = 0.2, upper = 1.5)}

\CommentTok{\# plot(DATA[, .(tsy, (1 + trend\_apply(tsy) * trend\_factor))])}

\NormalTok{DTdaily }\OtherTok{\textless{}{-}}\NormalTok{ DATA[,}
\NormalTok{                .(}
                  \AttributeTok{glo\_Sum    =} \FunctionTok{sum}\NormalTok{(Low\_B.Low\_W.glo),}
                  \AttributeTok{GLB\_Sum    =} \FunctionTok{sum}\NormalTok{(wattGLB),}
                  \AttributeTok{GLB\_N      =} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wattGLB)),}
                  \AttributeTok{DayLength  =} \FunctionTok{max}\NormalTok{(DayLength),}
                  \AttributeTok{En\_Ref\_sum =} \FunctionTok{sum}\NormalTok{(Enhanc\_C\_4\_ref),}
                  \AttributeTok{Thresh\_sum =} \FunctionTok{sum}\NormalTok{(Thresh\_test),}
\NormalTok{                  .N}
\NormalTok{                ),}
\NormalTok{                by }\OtherTok{=}\NormalTok{ Day]}

\FunctionTok{hist}\NormalTok{(DTdaily}\SpecialCharTok{$}\NormalTok{GLB\_N)}
\FunctionTok{hist}\NormalTok{(DTdaily[, GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength])}
\CommentTok{\# plot(DTdaily[, GLB\_N/DayLength, Day])}
\FunctionTok{summary}\NormalTok{(DTdaily[, GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength])}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot}\NormalTok{(DTdaily[, En\_Ref\_sum, Day])}
\FunctionTok{plot}\NormalTok{(DTdaily[, glo\_Sum, Day])}
\FunctionTok{plot}\NormalTok{(DTdaily[, GLB\_Sum, Day])}

\DocumentationTok{\#\# remove days with few relative data}
\NormalTok{Daytime\_Ratio }\OtherTok{\textless{}{-}} \FloatTok{0.3}

\NormalTok{DTdaily }\OtherTok{\textless{}{-}}\NormalTok{ DATA[,}
\NormalTok{                .(}
                  \AttributeTok{glo\_Sum    =} \FunctionTok{sum}\NormalTok{(Low\_B.Low\_W.glo),}
                  \AttributeTok{GLB\_Sum    =} \FunctionTok{sum}\NormalTok{(wattGLB),}
                  \AttributeTok{GLB\_N      =} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wattGLB)),}
                  \AttributeTok{DayLength  =} \FunctionTok{max}\NormalTok{(DayLength),}
                  \AttributeTok{En\_Ref\_sum =} \FunctionTok{sum}\NormalTok{(Enhanc\_C\_4\_ref),}
                  \AttributeTok{Thresh\_sum =} \FunctionTok{sum}\NormalTok{(Thresh\_test),}
\NormalTok{                  .N}
\NormalTok{                ),}
\NormalTok{                by }\OtherTok{=}\NormalTok{ Day]}

\NormalTok{DTyear }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}\AttributeTok{glo =} \FunctionTok{mean}\NormalTok{(Low\_B.Low\_W.glo),}
                   \AttributeTok{GLB =} \FunctionTok{mean}\NormalTok{(wattGLB),}
                   \AttributeTok{Ref =} \FunctionTok{mean}\NormalTok{(Enhanc\_C\_4\_ref),}
                   \AttributeTok{Thr =} \FunctionTok{mean}\NormalTok{(Thresh\_test),}
\NormalTok{                   .N),}
\NormalTok{               by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date))]}

\FunctionTok{plot}\NormalTok{(DTyear[, N, year], }\AttributeTok{col =} \StringTok{"blue"}\NormalTok{)}

\FunctionTok{plot}\NormalTok{(DTyear[, GLB}\SpecialCharTok{/}\NormalTok{glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\StringTok{"Clear GLB / CS libratran yearly means"}\NormalTok{)}

\FunctionTok{plot}\NormalTok{(DTyear[, Ref}\SpecialCharTok{/}\NormalTok{GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\StringTok{"Threshold ref / Clear Global yearly means"}\NormalTok{)}

\FunctionTok{plot}\NormalTok{(DTyear[, Ref}\SpecialCharTok{/}\NormalTok{glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\StringTok{"Threshold ref / CS libratran yearly means"}\NormalTok{)}

\FunctionTok{plot}\NormalTok{(DTyear[, Thr}\SpecialCharTok{/}\NormalTok{GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\FunctionTok{paste}\NormalTok{(}\StringTok{"Threshold / global yearly means"}\NormalTok{, trend\_factor))}

\NormalTok{ff }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x) \{}
    \FunctionTok{plot}\NormalTok{(DTyear[, }\DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ x }\SpecialCharTok{*}\NormalTok{ Thr}\SpecialCharTok{/}\NormalTok{GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{, }\AttributeTok{main =}\NormalTok{ x)}
\NormalTok{    DTyear[, }\FunctionTok{sum}\NormalTok{(}\FunctionTok{abs}\NormalTok{(}\DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ x }\SpecialCharTok{*}\NormalTok{ Thr}\SpecialCharTok{/}\NormalTok{GLB))]}
\NormalTok{\}}

\FunctionTok{optimize}\NormalTok{(ff, }\FunctionTok{c}\NormalTok{(.}\DecValTok{5}\NormalTok{, }\FloatTok{1.5}\NormalTok{), }\AttributeTok{tol =} \FloatTok{0.001}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
$minimum
[1] 0.8590668

$objective
[1] 0.6771877
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{ff}\NormalTok{(}\FloatTok{0.85}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
[1] 0.7037762
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot}\NormalTok{(DTyear[, GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{plot}\NormalTok{(DTyear[, Thr, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{plot}\NormalTok{(DTyear[, glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{plot}\NormalTok{(DTyear[, Ref, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}

\FunctionTok{rmserr}\NormalTok{(DTyear}\SpecialCharTok{$}\NormalTok{GLB, DTyear}\SpecialCharTok{$}\NormalTok{Thr)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
$mae
[1] 97.55895

$mse
[1] 9799.437

$rmse
[1] 98.9921

$mape
[1] 0.1680595

$nmse
[1] 46.16276

$rstd
[1] 0.1700543
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{DTmonth }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}\AttributeTok{glo =} \FunctionTok{mean}\NormalTok{(Low\_B.Low\_W.glo),}
                    \AttributeTok{GLB =} \FunctionTok{mean}\NormalTok{(wattGLB),}
                    \AttributeTok{Thr =} \FunctionTok{mean}\NormalTok{(Thresh\_test),}
\NormalTok{                    .N),}
\NormalTok{                by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date), }\FunctionTok{month}\NormalTok{(Date))]}
\NormalTok{DTmonth[, tsy }\SpecialCharTok{:=}\NormalTok{ year }\SpecialCharTok{+}\NormalTok{ (month }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)}\SpecialCharTok{/}\DecValTok{12}\NormalTok{ ]}

\CommentTok{\# plot(  DTmonth[, .N, tsy], col = "blue")}
\FunctionTok{plot}\NormalTok{(  DTmonth[, GLB}\SpecialCharTok{/}\NormalTok{glo, tsy], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\StringTok{"Clear GLB / CS libratran by month"}\NormalTok{)}

\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{out.height =} \StringTok{"32\%"}\NormalTok{   )}

\CommentTok{\# for (ad in sort(days)) \{}
\CommentTok{\#   temp \textless{}{-} DATA[Day == ad,]}
\CommentTok{\#}
\CommentTok{\#   ylim \textless{}{-} range(temp[, Low\_B.Low\_W.glo, wattGLB])}
\CommentTok{\#}
\CommentTok{\#   plot(  temp[, Low\_B.Low\_W.glo, Date],}
\CommentTok{\#          col = "blue",}
\CommentTok{\#          ylim = ylim)}
\CommentTok{\#   points(temp[, wattGLB, Date], col = "green")}
\CommentTok{\#   title(as.Date(ad, origin = "1970{-}01{-}01"))}
\CommentTok{\# \}}
\end{Highlighting}
\end{Shaded}
